A Data-Driven Framework for Neural Field Modeling

### 2011-01-02 ltx/first_order_framework/LaTeX_Manuscript.tex
editted sampling theorem derivation

\newcommand{\dean}[1]{\textsf{\emph{\textbf{\textcolor{red}{#1}}}}}

@@

\section{Derivation of Sampling Theorem}\label{App:SamplingTheorem}
\dean{This appendix provides a derivation for equations~\ref{eq:MinimumSensorDistance} and \ref{eq:BasisFunctionSeparation}. The derivation is adapted from \citet{Sanner1992} and \citet{Scerri2009}. Consider the cortical sheet defined on the surface $\Omega$ with sensors placed on a regular grid at positions $\mathbf{r}_n$ (where $n=0,...,n_y-1$ indexes the sensors) that are separated by the distance $\Delta_y$. The observations can be considered samples from a continuous field that is filtered (convolved) with the observation kernel described by
\begin{equation}
	y(\mathbf{r}_n)=\sum_{n=0}^{n_y-1}\delta(\mathbf r - \mathbf{r}_n ) v_m(\mathbf{r}),
\end{equation} 
where $v_m(\mathbf{r}) = v_t(\mathbf{r})\ast m(\mathbf{r})$. The Fourier transform of $y(\mathbf{r}_n)$ is
\begin{align}
 Y(\boldsymbol{\nu}) &= \frac{1}{\Delta_y^2}\sum_{n=0}^{n_y-1} \delta\left(\boldsymbol{\nu}-\frac{n}{\Delta_y}\right) \ast V_m(\boldsymbol \nu) \\
	&= \frac{1}{\Delta_y^2}V_m(\boldsymbol\nu)+\frac{1}{\Delta_y^2}\sum_{n=1}^{n_y-1} V_m\left(\boldsymbol{\nu}-\frac{n}{\Delta_y}\right).
\end{align} 
It should be clear that $Y(\boldsymbol{\nu})$ contains $V_m(\boldsymbol\nu)$ plus $n_y-1$ copies (aliases) of $V_m(\boldsymbol\nu)$ repeated on the regular lattice, where each copy is centered at $n\Delta_y^{-1}$. Due to the lowpass action of the observation kernel, the filtered dynamic field is band-limited with a cutoff frequency $\boldsymbol\nu_{cy}$. In order for $V_m(\boldsymbol\nu)$ to be disjointed from its aliases, the amount of shift $\Delta_y^{-1}$ must be at least $2\boldsymbol\nu_{cy}$, since each alias has a spectral range of
\begin{equation}
	\boldsymbol\nu = \left[\frac{n}{\Delta_y}-\boldsymbol{\nu}_{cy},\frac{n}{\Delta_y}+\boldsymbol{\nu}_{cy}\right].
\end{equation}
Therefore, to avoid aliasing the distance between observations must satisfy
\begin{equation}\label{eq:SamplingCriteria}
	\frac{1}{\Delta_y} \ge 2\boldsymbol{\nu}_{cy}.
\end{equation}
Since the observation kernel is not an ideal filter, an oversampling parameter should be included to further separate the aliases. Rearranging equation~\ref{eq:SamplingCriteria} and adding the oversampling parameter, $\rho$, gives
\begin{equation}\label{ap:Shannon}
	\Delta_y\le\frac{1}{2\rho\boldsymbol{\nu}_{cy}},
\end{equation}
where $\rho \in \mathbb{R} \ge 1$.}

>>>>

% \newcommand{\dean}[1]{\textsf{\emph{\textbf{\textcolor{red}{#1}}}}}
\newcommand{\dean}[1]{\textcolor{red}{#1}}

 \newcommand{\parham}[1]{\textsf{\emph{\textbf{\textcolor{blue}{#1}}}}}

@@

\section{Derivation of Sampling Theorem}\label{App:SamplingTheorem}
\dean{This appendix provides a derivation for equations~\ref{eq:MinimumSensorDistance} and \ref{eq:BasisFunctionSeparation}. The derivation is adapted from \citet{Sanner1992} and \citet{Scerri2009}. Consider the cortical sheet defined on the surface $\Omega$ with sensors placed on a regular grid at positions $\mathbf{r}_n$ (where $n=0,...,n_y-1$ indexes the sensors) that are separated by the distance $\Delta_y$. Noise-free observations can be considered samples from a continuous field that is filtered (convolved) with the observation kernel described by
\begin{equation}
	y(\mathbf{r}_n)=\sum_{n=0}^{n_y-1}\delta(\mathbf r - \mathbf{r}_n ) v_m(\mathbf{r}),
\end{equation} 
\parham{\begin{equation}
	\mathbf y=\sum_{n=0}^{n_y-1}\delta(\mathbf r - \mathbf{r}_n ) v_m(\mathbf{r}),
\end{equation}}
where $v_m(\mathbf{r}) = v_t(\mathbf{r})\ast m(\mathbf{r})$. The Fourier transform of \parham{$\mathbf y$~}$y(\mathbf{r}_n)$ is
\begin{align}
 Y(\boldsymbol{\nu}) &= \frac{1}{\Delta_y^2}\sum_{n=0}^{n_y-1} \delta\left(\boldsymbol{\nu}-\frac{\mathbf{n}_n}{\Delta_y}\right) \ast V_m(\boldsymbol \nu) \\
	&= \frac{1}{\Delta_y^2}V_m(\boldsymbol\nu) + \frac{1}{\Delta_y^2} \sum_{n=1}^{n_y-1} V_m\left(\boldsymbol{\nu}-\frac{\mathbf{n}_n}{\Delta_y}\right),
\end{align} 
where $\mathbf{n}$ is a $n_y \times 2$ matrix, spatially indexing the sensors (the columns are different spatial dimensions such that $\mathbf{r}_n = \Delta_y \mathbf{n}$). It should be clear that $Y(\boldsymbol{\nu})$ contains $V_m(\boldsymbol\nu)$ plus $n_y-1$ copies (aliases) of $V_m(\boldsymbol\nu)$ repeated on the regular lattice, where each copy is centered at $n\Delta_y^{-1}$. Due to the lowpass action of the observation kernel, the filtered dynamic field is band-limited with a cutoff frequency $\boldsymbol\nu_{cy}$. In order for $V_m(\boldsymbol\nu)$ to be disjointed from its aliases, the amount of shift $\Delta_y^{-1}$ must be at least $2\boldsymbol\nu_{cy}$, since each alias has a spectral range of
\begin{equation}
	\boldsymbol\nu = \left[\frac{n}{\Delta_y}-\boldsymbol{\nu}_{cy},\frac{n}{\Delta_y}+\boldsymbol{\nu}_{cy}\right].
\end{equation}
Therefore, to avoid aliasing the distance between observations must satisfy
\begin{equation}\label{eq:SamplingCriteria}
	\frac{1}{\Delta_y} \ge 2\boldsymbol{\nu}_{cy}.
\end{equation}
Since the observation kernel is not an ideal filter, an oversampling parameter should be included to further separate the aliases. Rearranging equation~\ref{eq:SamplingCriteria} and adding the oversampling parameter, $\rho$, gives
\begin{equation}\label{ap:Shannon}
	\Delta_y\le\frac{1}{2\rho\boldsymbol{\nu}_{cy}},
\end{equation}
where $\rho \in \mathbb{R} \ge 1$.}
